Importance sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-04-20 draft_p2.tex
Change \overline to \langle \rangle in caption for autocorr_drag
Updates figure illustr_ecoulement and justification for 2D in main text

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{illustr_vort/illustration_vorticity_tf2.png}
  \caption{Our case study is a grid-generated turbulent flow impinging a squared obstacle located at the center of a channel (in two dimensions).  The vorticity is displayed with an arbitrary colormap from blue (negative values) to red (positive values). The Reynolds number based on the grid spacing is $Re=...$.  // no color bar, show the grid //}
  \label{fig:computational_domain}
\end{figure}

The drag exerted by a grid-generated turbulent flow onto a squared obstacle is considered as our representative case study. The flow is contained in a long channel as illustrated in Fig.~\ref{fig:computational_domain}. Although real-world applications would eventually imply three-dimensional dynamics, a simplified two-dimensional setting has been chosen here to reduce the computational cost and make possible a systematic study. 
Nevertheless, this fluid-mechanical system exhibits the characteristic features of turbulent fluid-structure interaction. // true even if 2d? // In the present situation, the obstacle does not deform or move. Through  this specific setting, our main motivation is to evaluate the operability of importance sampling techniques to capture extreme events with a significant run-time savings.  
\\

@@

Drag fluctuations have been sampled along a long simulation of duration $T_{tot} = 4\times 10^6~\tau_0$, which will be referred to as the \textit{control run} in the following.
The corresponding estimate of the \ac{pdf} of drag fluctuations is shown in figure~\ref{fig:pdf_drag_a}.
It deviates from a normal law and shows an exponential tail for large positive fluctuations, \textit{i.e.}  ${\cal P}(f_d) = \lambda^{-1}e^{-\lambda f_d}$.
%
Fig.~\ref{fig:pdf_drag_a} also displays the \ac{pdf} of drag fluctuations acting on a control surface equivalent to the periphery of the obstacle but in the absence of the obstacle. 
%
In that case, the \ac{pdf} is quasi-symmetric and does not display exponential tails, indicating that the asymmetry of the \ac{pdf} and the development of positive exponential tail are closely related to the no-slip condition on the obstacle.
\begin{figure}
  \centering
    \subfloat[\ac{pdf} of drag fluctuations around mean.]
    {\label{fig:pdf_drag_a}
    	\includegraphics[width=.45\linewidth]{./PDF_drag/PDF_drag.png}}
    \subfloat[Autocorrelation of drag.]
    {\label{fig:pdf_drag_b}
    	\includegraphics[width=.45\linewidth]{./autocorr_drag/autocorr_drag.png}}  
      \caption{\textbf{(a)} Estimate of the zero-mean \ac{pdf} for drag fluctuations $f'_d = (f_d - \bar{f_d})$ where $\bar{f_d}$ denotes the averaged value. The drag is evaluated both in the presence and absence of the obstacle. Note that both \acsp{pdf} have different variance, and are here not normalized.
  \textbf{(b)} Autocorrelation function of the drag defined as $\left( \overline{f_d(t+\tau)f_d(t)}-\overline{f_d}^2 \right) /\sigma^2$. The lag $\tau$ is normalized by the turnover-time~\eqref{eq:turnover_time}.}
  \label{fig:pdf_drag}
\end{figure}
%
Lastly, the autocorrelation function of the drag is shown in Fig.~\ref{fig:pdf_drag_b}. It is found drag fluctuations are correlated over a time scale of the order of $\tau_0$, suggesting that the drag signal looses its memory typically after the sweeping of a few eddies past the obstacle.
%
This observation has important consequences for the application of rare event algorithms, as will be discussed in section~\ref{sec:rare_events_algorithms}.
%
In the following we define the \textit{correlation time} $\tau_c = 4\tau_0$.
Note that the ratio $tau_0 / tau_c$ may be viewed as a \textit{Strouhal number} $St$.
A value $St=0.25$ is consistent with commonly observed values for flows past blunt structures.

@@

% Introduction to AMS
The \acl{ams}~\cite{amspaper} inherits from the basic ideas of \textit{splitting} algorithms~\cite{kahnharris}: the sampling of a rare event is made easier by splitting the corresponding dynamical path into a sequence of events that can be sampled with a higher probability~\cite{glasserman,rolland_simonnet}.
Over the past ten years the \ac{AMS} has been successfully applied to a large body of problems, including the computation of the dissociation time of biomolecules~\cite{teo2016} or the simulation of rare relaminarizations in a stochastic model of wall turbulence~\cite{rolland2017}.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{illustr_ecoulement/illustr_ecoulement}
  \caption{Our case study is a grid-generated turbulent flow impinging a squared obstacle located at the center of a channel (in two dimensions).  The vorticity is displayed with an arbitrary colormap from blue (negative values) to red (positive values). The Reynolds number based on the grid spacing is $Re=...$.}
  \label{fig:illustr_ecoulement}
\end{figure}

The drag exerted by a grid-generated turbulent flow onto a squared obstacle is considered as our representative case study.
The flow is contained in a long channel as illustrated in Fig.~\ref{fig:illustr_ecoulement}.
Although real-world applications would eventually imply three-dimensional dynamics, a simplified two-dimensional setting has been chosen here to reduce the computational cost and make possible a systematic study. 
Nevertheless, this fluid-mechanical system embeds the key features that makes the application of rare event algorithms both relevant and challenging for turbulent fluid-structure interaction problems.
In particular, spatio-temporal chaos that results in the unpredictable emergence of coherent fluid structures, in turn leading to  strong fluctuations of the mechanical efforts on the structure.
In the present situation, the obstacle does not deform or move.
Through  this specific setting, our main motivation is to evaluate the operability of importance sampling techniques to capture extreme events with a significant run-time savings.  
\\

@@

Drag fluctuations have been sampled along a long simulation of duration $T_{tot} = 4\times 10^6~\tau_0$, which will be referred to as the \textit{control run} in the following.
The corresponding estimate of the \ac{pdf} of drag fluctuations is shown in figure~\ref{fig:pdf_drag_a}.
It deviates from a normal law and shows an exponential tail for large positive fluctuations, \textit{i.e.}  ${\cal P}(f_d) = \lambda^{-1}e^{-\lambda f_d}$.
%
Fig.~\ref{fig:pdf_drag_a} also displays the \ac{pdf} of drag fluctuations acting on a control surface equivalent to the periphery of the obstacle but in the absence of the obstacle. 
%
In that case, the \ac{pdf} is quasi-symmetric and does not display exponential tails, indicating that the asymmetry of the \ac{pdf} and the development of positive exponential tail are closely related to the no-slip condition on the obstacle.
\begin{figure}
  \centering
    \subfloat[\ac{pdf} of drag fluctuations around mean.]
    {\label{fig:pdf_drag_a}
    	\includegraphics[width=.45\linewidth]{./PDF_drag/PDF_drag.png}}
    \subfloat[Autocorrelation of drag.]
    {\label{fig:pdf_drag_b}
    	\includegraphics[width=.45\linewidth]{./autocorr_drag/autocorr_drag.png}}  
      \caption{\textbf{(a)} Estimate of the zero-mean \ac{pdf} for drag fluctuations $f'_d = (f_d - \bar{f_d})$ where $\bar{f_d}$ denotes the averaged value. The drag is evaluated both in the presence and absence of the obstacle. Note that both \acsp{pdf} have different variance, and are here not normalized.
  \textbf{(b)} Autocorrelation function of the drag defined as $\left( \langle f_d(t+\tau)f_d(t) \rangle-\langle f_d \rangle ^2 \right) /\sigma^2$. The lag $\tau$ is normalized by the turnover-time~\eqref{eq:turnover_time}.}
  \label{fig:pdf_drag}
\end{figure}
%
Lastly, the autocorrelation function of the drag is shown in Fig.~\ref{fig:pdf_drag_b}. It is found drag fluctuations are correlated over a time scale of the order of $\tau_0$, suggesting that the drag signal looses its memory typically after the sweeping of a few eddies past the obstacle.
%
This observation has important consequences for the application of rare event algorithms, as will be discussed in section~\ref{sec:rare_events_algorithms}.
%
In the following we define the \textit{correlation time} $\tau_c = 4\tau_0$.
Note that the ratio $tau_0 / tau_c$ may be viewed as a \textit{Strouhal number} $St$.
A value $St=0.25$ is consistent with commonly observed values for flows past blunt structures.

@@

% Introduction to AMS
The \acl{ams}~\cite{amspaper} inherits from the basic ideas of \textit{splitting} algorithms~\cite{kahnharris}: the sampling of a rare event is made easier by splitting the corresponding dynamical path into a sequence of events that can be sampled with a higher probability~\cite{glasserman,rolland_simonnet}.
Over the past ten years the \ac{ams} has been successfully applied to a large body of problems, including the computation of the dissociation time of biomolecules~\cite{teo2016} or the simulation of rare relaminarizations in a stochastic model of wall turbulence~\cite{rolland2017}.
